---
title: "Applications"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(tidyverse)
library(shiny)
library(shinythemes)
library(DT)
```

# Examples

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.

## Some simple app with a slider input

```{r}

shinyApp(
  ui = fluidPage(
        sliderInput(inputId = "num",
                label = "Choose a number",
                value = 50, min = 1, max = 100),
        plotOutput("hist")
    
   ),
  
    

  server = function(input, output) {
    output$hist <- renderPlot({
      title <- "Normalverteilung"
      hist(rnorm(input$num), main = title)
    })
  },

  options = list(height = 500)
)

```

## Interaktive histogram 

```{r}

shinyApp(
  ui <- fluidPage(

  # App title ----
  titlePanel("First app!"),

  # Sidebar layout with input and output definitions ----
  sidebarLayout(

    # Sidebar panel for inputs ----
    sidebarPanel(

      # Input: Slider for the number of bins ----
      sliderInput(inputId = "bins",
                  label = "Number of bins:",
                  min = 1,
                  max = 50,
                  value = 30)

    ),

    # Main panel for displaying outputs ----
    mainPanel(

      # Output: Histogram ----
      plotOutput(outputId = "distPlot")

    )
  )
),
server <- function(input, output) {

  # Histogram of the Old Faithful Geyser Data ----
  # with requested number of bins
  # This expression that generates a histogram is wrapped in a call
  # to renderPlot to indicate that:
  #
  # 1. It is "reactive" and therefore should be automatically
  #    re-executed when inputs (input$bins) change
  # 2. Its output type is a plot
  output$distPlot <- renderPlot({

    x    <- faithful$waiting
    bins <- seq(min(x), max(x), length.out = input$bins + 1)

    hist(x, breaks = bins, col = "#75AADB", border = "white",
         xlab = "Waiting time to next eruption (in mins)",
         main = "Histogram of waiting times")

    })

},
options = list(height = 500)
)


```

## Show data in a table 


 
```{r}


my_forecast <- readRDS("my_forecast.Rds")

shinyApp(
 ui <- fluidPage(

  # App title ----
  titlePanel("Shiny Text"),

  # Sidebar layout with a input and output definitions ----
  sidebarLayout(

    # Sidebar panel for inputs ----
    sidebarPanel(

      # Input: Selector for choosing dataset ----
      selectInput(inputId = "dataset",
                  label = "Choose a dataset:",
                  choices = c("forecast", "rock")),

      # Input: Numeric entry for number of obs to view ----
      numericInput(inputId = "obs",
                   label = "Number of observations to view:",
                   value = 10)
    ),

    # Main panel for displaying outputs ----
    mainPanel(

      # Output: Verbatim text for data summary ----
      verbatimTextOutput("summary"),

      # Output: HTML table with requested number of observations ----
      tableOutput("view")

    )
  )
),

# Define server logic to summarize and view selected dataset ----
server <- function(input, output) {

  # Return the requested dataset ----
  datasetInput <- reactive({
    switch(input$dataset,
           "forecast" = my_forecast,
           "rock" = rock)
  })

  # Generate a summary of the dataset ----
  output$summary <- renderPrint({
    dataset <- datasetInput()
    summary(dataset)
  })

  # Show the first "n" observations ----
  output$view <- renderTable({
    head(datasetInput(), n = input$obs)
  })

},
options = list(height = 1000)
)

```

## Some interactive plot with our dataset

```{r}

shinyApp(
  ui <- fluidPage(
    #App title
    titlePanel("Test App"),
    
    #Sidebar Layout
    sidebarLayout(
      sidebarPanel(
        
        #Input Auswahl für y-achse im User Interface
        selectInput(inputId = "variable",
                    label = "Was möchten sie auf der y-achse sehen?",
                    choices = colnames(my_forecast),
                    selected = "temp"),
        #Input Auswahl für die 3. Eigenschaft
        selectInput(inputId = "variable2",
                    label = "Was möchten sie auf der z-achse sehen?",
                    choices = colnames(my_forecast),
                    selected = "pressure"),
        # Input Auswahl für die Ploteigenschaften
        selectInput(inputId = "variable3",
                    label = "Choose the visualization",
                    choices = c("colour" = "colour", "size" = "size"),
                    selected = "color"),
        # Checkbox für den Datatable zum Auswählen der Attribute
        checkboxGroupInput("show_vars", "Columns in my_forecast to show:",
                           names(my_forecast), selected = "temp")
        ),
      mainPanel(
        # Output Festlegung für das User Interface
        plotOutput(outputId = "dia"),
        DT::dataTableOutput(outputId = "table")
      )
    )  
  ),
  server <- function(input, output){
    # Variable für die y-Achse wird geswitcht
    variableInput <- reactive({
      switch(input$variable,
             "temp" = my_forecast$temp,
             "pressure" = my_forecast$pressure,
             "humidity" = my_forecast$humidity,
             "temp_min" = my_forecast$temp_min,
             "temp_max" = my_forecast$temp_max,
             "weather_id" = my_forecast$weather_id,
             "weather_main" = my_forecast$weather_main,
             "weather_description" = my_forecast$weather_description,
             "weather_icon" = my_forecast$weather_icon,
             "wind_speed" = my_forecast$wind_speed,
             "wind_deg" = my_forecast$wind_deg,
             "clouds_all" = my_forecast$clouds_all,
             "dt" = my_forecast$dt,
             "sea_level" = my_forecast$sea_level,
             "grnd_level" = my_forecast$grnd_level,
             "temp_kf" = my_forecast$temp_kf,
             "rain_3h" = my_forecast$rain_3h,
             "sys_pod" = my_forecast$sys_pod,
             "dt_txt" = my_forecast$dt_txt
             )
    })
    # Variable für die 3. Eigenschaft
    variableInput2 <- reactive({
      switch(input$variable2,
             "temp" = my_forecast$temp,
             "pressure" = my_forecast$pressure,
             "humidity" = my_forecast$humidity,
             "temp_min" = my_forecast$temp_min,
             "temp_max" = my_forecast$temp_max,
             "weather_id" = my_forecast$weather_id,
             "weather_main" = my_forecast$weather_main,
             "weather_description" = my_forecast$weather_description,
             "weather_icon" = my_forecast$weather_icon,
             "wind_speed" = my_forecast$wind_speed,
             "wind_deg" = my_forecast$wind_deg,
             "clouds_all" = my_forecast$clouds_all,
             "dt" = my_forecast$dt,
             "sea_level" = my_forecast$sea_level,
             "grnd_level" = my_forecast$grnd_level,
             "temp_kf" = my_forecast$temp_kf,
             "rain_3h" = my_forecast$rain_3h,
             "sys_pod" = my_forecast$sys_pod,
             "dt_txt" = my_forecast$dt_txt
             )
    })
    # Versuch die Ploteinstellungen zu switchen
    variableInput3 <- reactive({
      switch(input$variable3,
             "colour" = colour,
             "size" = size
             )
    })
   
        
        
   # reaktives Rendern vom Plot
    output$dia <- renderPlot({
      ggplot(my_forecast, aes(x = dt_txt, y = variableInput()))+
        geom_point(aes(size = variableInput2())) 
    })
    # reaktives anzeigen vom DataTable
    output$table <- renderDataTable({
    DT::datatable(my_forecast[, input$show_vars, drop = FALSE])
    })
    
  },
options = list(height = 1000)
  
)



```
